---
title: "Demographic Information"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---

## Load Data


```{r}

library(patchwork)
library(tidyverse)
library(knitr)
# library(ggplot2)

rm(list=ls())
OUPUTDATA_LOCATION = file.path(getwd(),"Data/MCS Data/Processed Data")

# Load Original Data 
load(file.path(OUPUTDATA_LOCATION,"/DataWithExclusionsNoImputations/df0_BothGroups_FINAL.Rdata"))


```

### Ethnicity

Cleaning required. They report ethnicity differently in Englamdf

```{r}

df0 = df0_BothGroups
Ethnicity_England = df0$S2_Ethnicity_England_BDCEEAA0 %>% 
                    dplyr::recode(   
                                  `1` = "White",
                                  `2` = "White",
                                  `3` = "White",
                                  
                                  `4` = "Mixed",
                                  `5` = "Mixed",
                                  `6` = "Mixed",
                                  `7` = "Mixed",
                                  
                                  `8` = "Indian",
                                  `9` = "Pakistani",
                                  `10` = "Bangladeshi",
                                  `11` = "Other",
                                  
                                  `12` = "Black",
                                  `13` = "Black",
                                  `14` = "Black",
                                  
                                  `15` = "Chinese",
                                  
                                  `95` = "Other",
                                  )

Ethnicity_Wales = df0$S2_Ethnicity_Wales_BDCEWAA0 %>% 
                    dplyr::recode(   
                                  `1` = "White",
                                  `2` = "White",
                                  `3` = "White",
                                  `4` = "White",
                                  
                                  `5` = "Mixed",
                                  `6` = "Mixed",
                                  `7` = "Mixed",
                                  `8` = "Mixed",
                                  
                                  `9` = "Indian",
                                  `10` = "Pakistani",
                                  `11` = "Bangladeshi",
                                  `12` = "Other",
                                  
                                  `13` = "Black",
                                  `14` = "Black",
                                  `15` = "Black",
                                  
                                  `16` = "Chinese",
                                  
                                  `95` = "Other",
                                  )
Ethnicity_Scotland = df0$S2_Ethnicity_Scotland_BDCESAA0 %>% 
                    dplyr::recode(   
                                  `1` = "White",
                                  `2` = "White",
                                  `3` = "White",
                                  `4` = "White",
                                  
                                  `5` = "Mixed",
                                  
                                  `6` = "Indian",
                                  `7` = "Pakistani",
                                  `8` = "Bangladeshi",
                                  
                                  `9` = "Chinese",
                                  
                                  `10` = "Other",
                                  
                                  `11` = "Black",
                                  `12` = "Black",
                                  `13` = "Black",
                                  
                                  `95` = "Other",
                                  )


Ethnicity_NI = df0$S2_Ethnicity_NI_BDCENAA0 %>% 
                    dplyr::recode(   
                                  `1` = "White",
                                  
                                  `2` = "Chinese",
                                  
                                  `3` = "White",
                                  `4` = "White",
                                  
                                  `5` = "Mixed",
                                  
                                  `6` = "Indian",
                                  `7` = "Pakistani",
                                  `8` = "Bangladeshi",
                                  
                                  `9` = "Chinese",
                                  
                                  `10` = "Other",
                                  
                                  `11` = "Black",
                                  `12` = "Black",
                                  `13` = "Black",
                                  
                                  `95` = "Other",
                                  )
Ethnicity_Matrix_original = 
                  cbind(
                    df0$S2_Ethnicity_England_BDCEEAA0,
                    df0$S2_Ethnicity_Wales_BDCEWAA0,
                    df0$S2_Ethnicity_Scotland_BDCESAA0,
                    df0$S2_Ethnicity_NI_BDCENAA0
                  )


Ethnicity_Matrix = cbind(Ethnicity_England,
                         Ethnicity_Wales,
                         Ethnicity_Scotland,
                         Ethnicity_NI)

# Ethnicity_Matrix %>%
#   apply(., 1, function(x) length(which(!is.na(x)))) %>%
#   table()

Country = Ethnicity_Matrix %>% 
            apply(.,1, function(x) which(!is.na(x))) %>%
            unlist()

Ethnicity = Ethnicity_Matrix %>% 
            apply(., 1, function(x) as.vector(na.omit(x))[1]) 

# Ethicity = Ethnicity_Matrix[]



# Check i haven't missed any codes 
# Ethnicity_Matrix_original %>%
#   as.data.frame() %>%
#   slice(which(apply(Ethnicity_Matrix,1,function(x) length(which(!is.na(x))))==0)) %>%
#   unlist(c(t(.))) %>%
#   table()

```

Table of ethnicity percentages. Note that there are missing values for `r length(which(is.na(Ethnicity)))` participants. 

```{r}

EthnicityTbl =
  Ethnicity %>% 
    table() %>% 
    data.frame() %>%
    dplyr::arrange(Freq) %>%
    dplyr::mutate(Percent = Freq/sum(Freq)*100)

EthnicityTbl  %>%
  kable(., digits = 2)

```


### Age

I couldn't find child age at interview data for MCS1 in the MCS1 data release, but it provided in harmonised BMI data release, with some missing data. 

For sweeps 5 & 6 I'm only given month/year of interview and birth, which may explain some odd looking peaks in the data.

```{r}

Age_Matrix = df0_BothGroups %>%
            dplyr::select(S1 = S1_Health_Age, S2=S2_Age, S5=S5_AgeAtInterview, S6=S6_Age_Est) %>%
            tidyr::pivot_longer(cols=S1:S6, values_to = "Age") 
            
AgePlot = 
ggplot(Age_Matrix, aes(x=Age)) + 
  geom_histogram(bins=150) + 
  jtools::theme_apa() + 
  labs(title="Child Age over the four MCS Sweeps",y="Frequency", x="Age At Interview") + 
  scale_x_continuous(minor_breaks =seq(0,16,by=.5),breaks=seq(0,16,by=1), labels=seq(0,16,by=1))

AgePlot
ggsave(file=file.path("Plots","AgeMCS.png"), device="png", width=6, height=3)

AgePlotTrimmed = 
  AgePlot + coord_cartesian(y=c(0,2000))

ggsave(plot=AgePlotTrimmed,file=file.path("Plots","AgeMCS_trimmed.png"), device="png", width=6, height=3)
```


#### Child Age Table

```{r}

Age_Matrix %>% 
  dplyr::group_by(name) %>%
  summarise(mean=mean(Age, na.rm=TRUE), 
            sd=sd(Age, na.rm=TRUE), 
            N_NotMissing = length(which(!is.na(Age)))) %>%
  kable(., digits=3)



```

### Gender


```{r}

colnames(df0_BothGroups)[grepl("imd",tolower(colnames(df0_BothGroups)))]

df0_BothGroups %>%
  dplyr::select(S1_Main_Sex,S2_Sex_bhcsex00,S2_Sex,S5_Sex_ECCSEX00) %>%
  tidyr::pivot_longer(cols=S1_Main_Sex:S5_Sex_ECCSEX00) %>%
  dplyr::group_by(name) %>%
  summarise(N_NotMissing = length(which(!is.na(value))))
  
df0_BothGroups %>% 
  dplyr::summarise(N_Male = length(which(S2_Sex_bhcsex00==1)),
                   N_Female = length(which(S2_Sex_bhcsex00==2)),
                   Percent_Male = N_Male /(N_Male + N_Female),
                   Percent_Female = N_Female /(N_Male + N_Female)
                   ) 
  # table(.) %>%
  # `names<-` (c("male", "female"))

```


### Geographic Data

Interview Country

```{r}
S1Geo = data.table::fread("Data/MCS Data/Raw Data/UKDA-4683-tab MCS1/tab/mcs1_geographically_linked_data.tab", stringsAsFactors = FALSE, data.table = FALSE)
S1Geo = S1Geo[match(df0_BothGroups$MCSID, S1Geo$mcsid),]

S1Geo %>%
  dplyr::mutate(country_new = dplyr::recode(aactry00,
                `1` = "England",
                `2` = "Wales",
                `3` = "Scotland",
                `4` = "Northern Ireland")) %>%
  group_by(country_new) %>% 
  summarise(N=n()) %>% 
  mutate(Perc = round(N/sum(N)*100, digits=2))

```

### Who were the responders in the first and second sweep of the study?

```{r}

ResponderTable = 
df0_BothGroups %>% 
  dplyr::select(S1_Main_Identity_AMDRES00,S2_Main_Identity_BMDRES00) %>%
  tidyr::pivot_longer(cols=S1_Main_Identity_AMDRES00:S2_Main_Identity_BMDRES00) %>%
  mutate(value = dplyr::recode(value, 
                               `1`= "Natural Mother",
                               `2`= "Natural Father",
                               `3`= "Adoptive Mother",
                               `5`= "Foster Mother",
                               `6`= "Foster Father",
                               `9`= "Grandmother")) %>% 
  dplyr::group_by(name) %>%
  summarise(N_Mother = length(which(value== "Natural Mother")),
            N_Father = length(which(value== "Natural Father")),
            N_Adoptive_Mother = length(which(value== "Adoptive Mother")),
            N_Foster_Mother = length(which(value== "Foster Mother")),
            N_Fother_Father = length(which(value== "Foster Father")),
            N_Grandmother = length(which(value== "Grandmother")),
            ) %>%
  dplyr::select(-name) %>%
  t() %>% 
  `colnames<-`((c("S1","S2"))) %>%
  dplyr::as_tibble(rownames = NA) %>%
  rownames_to_column() %>%
  mutate(S1_Percent = round(S1/sum(S1),4),
         S2_Percent = round(S2/sum(S2),3)) 
  
ResponderTable
    


# table(df0_BothGroups$S1_Main_Identity_AMDRES00)
# table(df0_BothGroups$S2_Main_Identity_BMDRES00)


```

### Responder Education Level 

Missing responder data for S1 is `r length(which(is.na(df0_BothGroups$S1_SES_EducationMain_AMDNVQ00) | df0_BothGroups$S1_SES_EducationMain_AMDNVQ00==-1 ))` and for S2 is `r length(which(is.na(df0_BothGroups$S2_Main_Education_BMDNVQ00) | df0_BothGroups$S2_Main_Education_BMDNVQ00==-1 ))`

```{r}
S1_Qualifications =
table(df0_BothGroups$S1_SES_EducationMain_AMDNVQ00) %>%
  .[-1] %>%
  `names<-`((c(paste0("NVQ Level ",1:5),"Other Qualification","No Qualifications"))) %>%
  rbind(., (./sum(.)) ) %>%
  rbind.data.frame(., cumsum(.[2,])) %>%
  `rownames<-`(c("freq", "prob", "cumprob"))


S2_Qualifications =
table(df0_BothGroups$S2_Main_Education_BMDNVQ00) %>%
  .[-1] %>%
  `names<-`((c(paste0("NVQ Level ",1:5),"Other Qualification","No Qualifications"))) %>%
  rbind(., (./sum(.)) ) %>%
  rbind.data.frame(., cumsum(.[2,])) %>%
  `rownames<-`(c("freq", "prob", "cumprob"))

S1_Qualifications
S2_Qualifications

```



### Employment Level

```{r}

S1Der = data.table::fread("Data/MCS Data/Raw Data/UKDA-4683-tab MCS1/tab/mcs1_derived_variables.tab", stringsAsFactors = FALSE, data.table = FALSE)
S1Der = S1Der[match(df0_BothGroups$MCSID, S1Der$MCSID),]

S1Der %>%
  dplyr::mutate(S1_Main_Employ = dplyr::recode(AMD07C00,
                                               `1` = "Hi manag/prof",
                                               `2` = "Lo manag/prof",
                                               `3` = "Intermediate",
                                               `4` = "Small emp and s-emp",
                                               `5` = "Low sup and tech",
                                               `6` = "Semi routine",
                                               `7` = "Routine",
                                               `-1` = "Not Applicaable",
                                               )) %>%
  ggplot(.,aes(x=S1_Main_Employ)) + 
  geom_bar() + 
  geom_text(stat='count', aes(label=..count..), vjust=-1) + 
  jtools::theme_apa() +
  labs(title="NS-SEC 7 (last known job) of Main Respondent at First Sweep", x=NULL, y="Count") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + 
  ylim(c(0000,3200))

S1Der$AMD07C00 %>%
  table() %>%
  rbind(., (./sum(.)) ) %>%
  rbind.data.frame(., cumsum(.[2,])) %>%
  `rownames<-`(c("freq", "prob", "cumprob")) %>%
  `colnames<-`(c("Not Applicaable","Hi manag/prof","Lo manag/prof","Intermediate","Small emp and s-emp","Low sup and tech","Semi routine","Routine")) %>%
  format(.,nsmall=5,digits=0)
  
  

```

### Proportion of drug use in samples

```{r}


drug_vars = c("S6_RiskyBehaviours_Cig","S6_RiskyBehaviours_ECig","S6_RiskyBehaviours_Alcohol","S6_RiskyBehaviours_Cannabis")

df0_BothGroups %>%
  dplyr::select(drug_vars) %>% 
  apply(.,2, table) %>% 
  kable(., caption="Frequecnies of Drug Use")

df0_BothGroups %>%
  dplyr::select(drug_vars) %>% 
  apply(.,2, table) %>% 
  apply(.,2, function(x) x/sum(x)) %>%
  kable(., caption="Frequecnies of Drug Use", digits=2)


```
