---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

### Load data 

```{r, warning=FALSE, results=FALSE, message=FALSE}

rm(list=ls())
source("Script P2S0 - Load Analysis Environment.R")
load(file.path("Output R Data", "cca_boot.Rdata"))
load(file.path("Output R Data", "cca_splithalf.Rdata"))
load(file.path("Output R Data", "cca_boot_teach.Rdata"))
load(file.path("Output R Data", "cca_splithalf_teacher.Rdata"))

```


# Analysis 0  - Hierarchial cluster analysis of variables

To simply aid visualisation, we have cluster the predictor and outcome variables into 4 (5 groups including teacher metrics)

```{r, echo=TRUE,results='hide',fig.keep='all'}

distances = stats::dist(t(df0_imputed_BothGroups[,outcomes]), method="manhattan")
  hclust_results = stats::hclust(distances)
  Outcome_Order = hclust_results$order
  Outcome_Ordered = outcomes[Outcome_Order]
  Outcome_Labels_Ordered = outcomes_labels[Outcome_Order]
  plot(hclust_results, hang=-1, main = "Hierarchial Clustering of Outcome Variables")
  Outcome_Cluster = stats::cutree(hclust_results, 4)
# sort(Outcome_Cluster)
  Outcome_Cluster_Labels = Convert(Outcome_Cluster,1:4,c("Behavioural Problems","Mental Health", "Drug-Use", "Cognition"))

# For ease of presentation, teacher's responses are not clustered in the usual way, but just tagged on to the above. 
  Outcome_Cluster2 = c(rep(0,6),Outcome_Cluster)
  Outcome_Ordered2 = c(outcomes2[1:6],Outcome_Ordered)
  Outcome_Labels_Ordered2 = c(outcomes_labels2[1:6],Outcome_Labels_Ordered)
  names(Outcome_Cluster2)[1:6] = outcomes2[1:6]
  Outcome_Cluster_Labels2 = Convert(Outcome_Cluster2,0:4,c("Teacher Ratings","Behavioural Problems","Mental Health", "Drug-Use", "Cognition"))

# not used in results  - but out of curiorsity looked at clustering all outcomes with teacher-reports
# 
#       hclust_results = hclust(dist(t(df0_imputed_Teach[,outcomes2]), method="manhattan"))
#       plot(hclust_results, hang=-1)

#Cluster Predictors
distances = dist(t(df0_imputed_group1[,envvar]), method="manhattan")
hclust_results = hclust(distances)
envvar_Order = hclust_results$order
envvar_Ordered = envvar[envvar_Order]
envvar_Labels_Ordered = envvar_labels[envvar_Order]
# plot(hclust_results, hang=-1)


```

### Plot All Outcomes

```{r results=FALSE, message=FALSE }
pdf(file=file.path("Plots","Histograms","histograms_variables_BothGroups.pdf"),height=42/2, width=15)
par(mfrow=c(11,5), mar=c(1,1,3,1))
for (i in c(envvar, outcomes)){
    hist(df0_imputed_BothGroups[,i], 
         col="grey", 
         main=c(envvar_labels, outcomes_labels)[match(i, c(envvar, outcomes))])
  }
dev.off()

pdf(file=file.path("Plots","Histograms","histograms_variables_group1.pdf"),height=42/2, width=15)
par(mfrow=c(11,5), mar=c(1,1,3,1))
for (i in c(envvar, outcomes)){
    hist(df0_imputed_group1[,i], 
         col="grey", 
         main=c(envvar_labels, outcomes_labels)[match(i, c(envvar, outcomes))])
  }
dev.off()

pdf(file=file.path("Plots","Histograms","histograms_variables_group2.pdf"),height=42/2, width=15)
par(mfrow=c(11,5), mar=c(1,1,3,1))
for (i in c(envvar, outcomes)){
    hist(df0_imputed_group2[,i], 
         col="grey", 
         main=c(envvar_labels, outcomes_labels)[match(i, c(envvar, outcomes))])
  }
dev.off()

#Teacher Datasets

pdf(file=file.path("Plots","Histograms","histograms_variables_combined_teach_BothGroups.pdf"),height=42/2, width=15)
par(mfrow=c(12,5), mar=c(1,1,3,1))
for (i in c(envvar, outcomes2)){
    hist(df0_imputed_Teach_BothGroups[,i], 
         col="grey", 
         main=c(envvar_labels, outcomes_labels2)[match(i, c(envvar, outcomes2))])
  }
dev.off()

pdf(file=file.path("Plots","Histograms","histograms_variables_combined_teach_group1.pdf"),height=42/2, width=15)
par(mfrow=c(12,5), mar=c(1,1,3,1))
for (i in c(envvar, outcomes2)){
    hist(df0_imputed_Teach_group1[,i], 
         col="grey", 
         main=c(envvar_labels, outcomes_labels2)[match(i, c(envvar, outcomes2))])
  }
dev.off()

pdf(file=file.path("Plots","Histograms","histograms_variables_combined_teach_group2.pdf"),height=42/2, width=15)
par(mfrow=c(12,5), mar=c(1,1,3,1))
for (i in c(envvar, outcomes2)){
    hist(df0_imputed_Teach_group2[,i], 
         col="grey", 
         main=c(envvar_labels, outcomes_labels2)[match(i, c(envvar, outcomes2))])
  }
dev.off()


```


### Figure 2

note to giacomo - fix axes! 

```{r}
PlotLoadings = function(dat, recode=FALSE, titletext=""){
  
  if (recode){
    dat = dat*-1
  }

  dat$negative = dat$original<0
  # dat[!dat$negative,1:4]=dat[!dat$negative,1:4]*-1
  dat$FancyLabels = all_var_labels2[match(rownames(dat),all_var2)]
  # dat$Group = factor(as.numeric(grepl("S[5-6]",dat$varlabel)), labels=c("Environmental Predictors","Outcome"))
  dat = dat[order(abs(dat$original)),]
  
  dat$errormin = dat$X2.5.
    dat$errormin[dat$negative] = dat$errormin[dat$negative]*-1
  dat$errormax = dat$X97.5
    dat$errormax[dat$negative] = dat$errormax[dat$negative]*-1
    
  
   plot=
    ggplot(dat, aes(x=1:nrow(dat), y=abs(original), fill=negative)) + geom_bar(stat="identity")  + 
      geom_errorbar(aes(ymin=errormin,ymax=errormax)) + 
    jtools::theme_apa() +
    coord_flip() + labs(y=NULL,x="") + theme(legend.position = "none") + scale_fill_manual(values=c( "#1B9E77", "#D95F02")) + 
    scale_x_continuous(breaks=1:nrow(dat),labels=dat$FancyLabels) +
    theme(text=element_text(family="serif")) + 
     geom_hline(aes( alpha=.9, yintercept=.1), linetype="dashed", col="grey") + 
    geom_hline(aes( alpha=.9, yintercept=0), linetype="dashed") + 
     labs(title=titletext)
   
  plot
  # facet_wrap(~Group,strip.position = "top", scales = "free", nrow=1, ncol=2) + theme(panel.spacing = unit(.3, "cm"), strip.background = element_blank()) +
  #  scale_x_continuous(breaks=1:nrow(dat),labels=dat$FancyLabels) 
  # 
  return(plot)
}


```


```{r, fig.height=13, fig.width=9}

p1 = PlotLoadings(cca_boot$xcoef_Quantiles[[1]], titletext = "ERF CCA Weights Comp1")
p2 = PlotLoadings(cca_boot$xcoef_Quantiles[[2]], titletext = "ERF CCA Weights Comp2")
p3 = PlotLoadings(cca_boot$xcoef_Quantiles[[3]], titletext = "ERF CCA Weights Comp3")

p4 = PlotLoadings(cca_boot$ycoef_Quantiles[[1]], titletext = "Outcome CCA Weights Comp1")
p5 = PlotLoadings(cca_boot$ycoef_Quantiles[[2]], titletext = "Outcome CCA Weights Comp2")
p6 = PlotLoadings(cca_boot$ycoef_Quantiles[[3]], titletext = "Outcome CCA Weights Comp3")

library(patchwork)
LoadingPlot = p1 + p2 + p3 + p4 + p5 + p6 + patchwork::plot_layout(ncol = 2, byrow = FALSE)
LoadingPlot 
ggsave(filename=file.path("Plots","LoadingsPlots_group1.pdf"),  LoadingPlot, device="pdf", width=9, height=13)
ggsave(filename=file.path("Plots","LoadingsPlots_group1.png"),  LoadingPlot, device="png", width=9, height=13, dpi=600)


rm(p1,p2,p3,p4,p5,p6,LoadingPlot)
```

### Supplementary Figure 3

```{r, fig.height=13, fig.width=9}

# cca_splithalf_procrustes$model_results

p1 = PlotLoadings(cca_boot_teach$xcoef_Quantiles[[1]], titletext = "ERF CCA Weights Comp1")
p2 = PlotLoadings(cca_boot_teach$xcoef_Quantiles[[2]], titletext = "ERF CCA Weights Comp2")
p3 = PlotLoadings(cca_boot_teach$xcoef_Quantiles[[3]], titletext = "ERF CCA Weights Comp3")

p4 = PlotLoadings(cca_boot_teach$ycoef_Quantiles[[1]], titletext = "Outcome CCA Weights Comp1")
p5 = PlotLoadings(cca_boot_teach$ycoef_Quantiles[[2]], titletext = "Outcome CCA Weights Comp2")
p6 = PlotLoadings(cca_boot_teach$ycoef_Quantiles[[3]], titletext = "Outcome CCA Weights Comp3")

library(patchwork)
LoadingPlot = p1 + p2 + p3 + p4 + p5 + p6 + patchwork::plot_layout(ncol = 2, byrow = FALSE)
LoadingPlot 
ggsave(filename=file.path("Plots","LoadingsPlots_teach.pdf"),  LoadingPlot, device="pdf", width=9, height=13)
ggsave(filename=file.path("Plots","LoadingsPlots_teach.png"),  LoadingPlot, device="png", width=9, height=13, dpi=600)

```



## Stacked bar chart figure  

### Figure 3

```{r}

PlotData = data.frame(cca_splithalf_procrustes$R2_matrix_BinaryOutcomes_Combined)
    PlotData[PlotData<0] = 0
    PlotData$Var = rownames(PlotData)
    PlotData = melt(PlotData,ID="Var")
    PlotData$variable = factor(PlotData$variable)
    PlotData$Cluster = (Outcome_Cluster_Labels2[match(PlotData$Var,outcomes2)])
    PlotData$Cluster[PlotData$Cluster=="Behavioural Problems"] = "Behav. Problems"
    PlotData$Cluster = factor(PlotData$Cluster)
    PlotData$Var = factor(PlotData$Var, levels=Outcome_Ordered2, labels=Outcome_Labels_Ordered2)
  #Fill Colour
FillCol = c(as.vector(  RColorBrewer::brewer.pal(5,"Dark2")), as.vector(wesanderson::wes_palette("Darjeeling1",n=5)))

PLOT3=
    ggplot(data=PlotData, aes(x=Var,y=value, fill=variable, group=Cluster)) + 
      geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="LM_R2",], fill="black") + 
      # geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="cc10",], fill=FillCol[10]) + 
      # geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="cc9",], fill=FillCol[9]) +        
      # geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="cc8",], fill=FillCol[8]) + 
      # geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="cc7",], fill=FillCol[7]) + 
      # geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="cc6",], fill=FillCol[6]) + 
      # geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="cc5",], fill=FillCol[5]) + 
      # geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="cc4",], fill=FillCol[4]) + 
      geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="cc3",], fill=FillCol[3]) + 
      geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="cc2",], fill=FillCol[1]) + 
      geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="cc1",], fill=FillCol[2]) + 
    labs(y=bquote('Variance Explained'~(r^2)), x="Outcome Variables") +
    facet_wrap(~Cluster,strip.position = "top", scales = "free_x", nrow=1) + theme(panel.spacing = unit(0, "cm"), strip.background = element_blank()) +
    jtools::theme_apa()+
    theme(axis.title.y.right = element_blank(),                # hide right axis title
          axis.text.y.right = element_blank(),                 # hide right axis labels
          axis.ticks.x = element_blank(),                      # hide left/right axis ticks
          axis.text.y = element_text(margin = margin(r = 0)),  # move left axis labels closer to axis
          #panel.spacing = unit(10, "mm"),                     # remove spacing between facets
          strip.background = element_blank(),                  # match default line size of theme_classic
          legend.position = "none",
          axis.text.x = element_text(angle = 90,hjust=0.95,vjust=0.2),
          text=element_text(family="serif")
    ) +
    scale_fill_manual(labels = unique(PlotData$variable),values=c( wesanderson::wes_palette("BottleRocket2",n=5),wesanderson::wes_palette("Darjeeling1",n=5)    )) +
    scale_y_continuous(breaks=c(0,5,10,15)/100, labels=c("0%","5%", "10%", "15%"))


ggsave(filename=file.path("Plots","VarianceExplained1.pdf"),  PLOT3, device="pdf", width=6, height=4)
ggsave(filename=file.path("Plots","VarianceExplained1.png"),  PLOT3, device="png", width=6, height=4, dpi=600)

PLOT3 #+ ylim(c(0,.19))

```

#### Supplementary Figure 4

```{r}
PlotData = data.frame(cca_splithalf_teacher$R2_matrix_BinaryOutcomes_Combined)
    PlotData[PlotData<0] = 0
    PlotData$Var = rownames(PlotData)
    PlotData = melt(PlotData,ID="Var")
    PlotData$variable = factor(PlotData$variable)
    PlotData$Cluster = (Outcome_Cluster_Labels2[match(PlotData$Var,outcomes2)])
    PlotData$Cluster[PlotData$Cluster=="Behavioural Problems"] = "Behav. Problems"
    PlotData$Cluster = factor(PlotData$Cluster)
    PlotData$Var = factor(PlotData$Var, levels=Outcome_Ordered2, labels=Outcome_Labels_Ordered2)

#Fill Colour
FillCol = c(as.vector(  RColorBrewer::brewer.pal(5,"Dark2")), as.vector(wesanderson::wes_palette("Darjeeling1",n=5)))

PLOT3=
    ggplot(data=PlotData, aes(x=Var,y=value, fill=variable, group=Cluster)) + 
      geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="LM_R2",], fill="black") + 
      # geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="cc10",], fill=FillCol[10]) + 
      # geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="cc9",], fill=FillCol[9]) +        
      # geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="cc8",], fill=FillCol[8]) + 
      # geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="cc7",], fill=FillCol[7]) + 
      # geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="cc6",], fill=FillCol[6]) + 
      # geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="cc5",], fill=FillCol[5]) + 
      # geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="cc4",], fill=FillCol[4]) + 
      geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="cc3",], fill=FillCol[3]) + 
      geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="cc2",], fill=FillCol[1]) + 
      geom_bar(position="identity",stat="identity", alpha=1, data=PlotData[PlotData$variable=="cc1",], fill=FillCol[2]) + 
    labs(y=bquote('Variance Explained'~(r^2)), x="Outcome Variables") +
    facet_wrap(~Cluster,strip.position = "top", scales = "free_x", nrow=1) + theme(panel.spacing = unit(0, "cm"), strip.background = element_blank()) +
    jtools::theme_apa()+
    theme(axis.title.y.right = element_blank(),                # hide right axis title
          axis.text.y.right = element_blank(),                 # hide right axis labels
          axis.ticks.x = element_blank(),                      # hide left/right axis ticks
          axis.text.y = element_text(margin = margin(r = 0)),  # move left axis labels closer to axis
          #panel.spacing = unit(10, "mm"),                       # remove spacing between facets
          strip.background = element_blank(),         # match default line size of theme_classic
          legend.position = "none",
          axis.text.x = element_text(angle = 90,hjust=0.95,vjust=0.2),
          text=element_text(family="serif")
    ) +
    scale_fill_manual(labels = unique(PlotData$variable),values=c( wesanderson::wes_palette("BottleRocket2",n=5),wesanderson::wes_palette("Darjeeling1",n=5)    )) + 
  scale_y_continuous(breaks=c(0,5,10,15)/100, labels=c("0%","5%", "10%", "15%"))

ggsave(filename=file.path("Plots","VarianceExplained_teach.pdf"),  PLOT3, device="pdf", width=8, height=4)
ggsave(filename=file.path("Plots","VarianceExplained_teach.png"),  PLOT3, device="png", width=8, height=4, dpi=600)

PLOT3 #+ ylim(c(0,.19))

```


# Supplementary Figure 2 

```{r}

# apply(A3_teach$R2_matrix,2,mean)
# apply(A3_teach$R2_matrix,2,mean)





```


#### Variance Explained in each outcome tables

Correlation Confidence Interval Fucntion 

```{r}

.CorrelationCIEstimator = function(r, n, alpha=0.05){
  Fr = base::atanh(r)                 # Fisher Z Transform
  SE = 1/((n-3)^.5)             # Standard Error
  CI = stats::qnorm(c(alpha/2,1-alpha/2), mean=Fr, sd=SE)
  CI = base::tanh(CI)
  # p  = (1-pnorm(abs(Fr), mean=0, sd=SE))*2    # Fisher Z P value
  t = r*base::sqrt((n-2)/(1-r^2))       # P-value estimated from t-distribution
  p  = (1-stats::pt(base::abs(t), df=n-2))*2
  return(base::list(CI=CI,p=p))
}

```


### Table 2

Variance Explained for each outcome variables

```{r}

absSquare = function(x){
  neg = x<0
  out = x^2
  out[neg] = out[neg]*-1
  return(out)
}



cc1 = cca_splithalf_procrustes$R2_matrix_BinaryOutcomes_Combined$cc1
# First CCA variate
# cc1_CI_LB = sapply(cc1, function(x) 
#                .CorrelationCIEstimator(x^.5, n=nrow(df0_imputed_group2), alpha=0.05)$CI[1])  #Need to convert R2 to R, which x^2 is used
# cc1_CI_UB = sapply(cc1, function(x) 
#                .CorrelationCIEstimator(x^.5, n=nrow(df0_imputed_group2), alpha=0.05)$CI[2])

# Second CCA variate
cc2 = cca_splithalf_procrustes$R2_matrix_BinaryOutcomes_Combined$cc2 
# cc2_CI_LB = sapply(cc2, function(x) 
#                .CorrelationCIEstimator(x^.5, n=nrow(df0_imputed_group2), alpha=0.05)$CI[1])
# cc2_CI_UB = sapply(cc2, function(x) 
#                .CorrelationCIEstimator(x^.5, n=nrow(df0_imputed_group2), alpha=0.05)$CI[2])

# Third CCA variate
cc3 = cca_splithalf_procrustes$R2_matrix_BinaryOutcomes_Combined$cc3
# cc3_CI_LB = sapply(cc3, function(x) 
#                .CorrelationCIEstimator(x^.5, n=nrow(df0_imputed_group2), alpha=0.05)$CI[1])
# cc3_CI_UB = sapply(cc3, function(x) 
#                .CorrelationCIEstimator(x^.5, n=nrow(df0_imputed_group2), alpha=0.05)$CI[2])

# Variance Explained by Linear MOdel
LM_VE = cca_splithalf_procrustes$R2_matrix_BinaryOutcomes_Combined$LM_R2


Table2 = 
cbind.data.frame(cc1, #absSquare(cc1_CI_LB), absSquare(cc1_CI_UB),
                 cc2, #absSquare(cc2_CI_LB), absSquare(cc2_CI_UB),
                 cc3, #absSquare(cc3_CI_LB), absSquare(cc3_CI_UB),
                 LM_VE
                 )

AverageVE = apply(Table2, 2, mean)
Table2 = rbind.data.frame(Table2, AverageVE)
  
Table2 %>% 
          # format(.,nsmall=3, digits=0) %>%
          # mutate_all(.,str_replace_all, pattern = "0\\.", replacement="\\.") %>%
          dplyr::slice(c(Outcome_Order,23)) %>% 
          `rownames<-`(c(Outcome_Labels_Ordered, "Mean")) %>% 
          `colnames<-`(c("cc1","cc2","cc3","LM")) %>%
          knitr::kable(digits=3)

Table2 %>%
          dplyr::slice(c(Outcome_Order,23)) %>% 
          `rownames<-`(c(Outcome_Labels_Ordered, "Mean")) %>% 
          `colnames<-`(c("cc1","cc2","cc3","LM")) %>%
          format(., digits=0, nsmall=3) %>%
          apply(., 2, function(x) sub("0\\.","\\.",x, perl=TRUE)) %>%
          write.csv(., file=file.path("Output R Data", "Table2.csv"), row.names = TRUE)

        


rm(cc1,#cc1_CI_LB,cc1_CI_UB,
   cc2,#cc2_CI_LB,cc2_CI_UB,
   cc3,#cc3_CI_LB,cc3_CI_UB,
  LM_VE
  )

```



```{r}

format(cca_splithalf_procrustes$R2_matrix_BinaryOutcomes_Combined, digits=0, nsmall=4)[,c(1:4,22,23)]

# format(cca_splithalf_teacher$R2_matrix_unbiased, digits=0, nsmall=4)[,c(1:4,23)]


```

```{r}

apply(cca_splithalf_procrustes$R2_matrix_BinaryOutcomes_Combined,1,which.max)



```


### Table 2 - Including Teacher Data

Variance Explained for each outcome variables - TEACHER DATA INCLUDED

```{r}

cc1 = cca_splithalf_teacher$R2_matrix_BinaryOutcomes_Combined$cc1
# First CCA variate
# cc1_CI_LB = sapply(cc1, function(x) 
#                .CorrelationCIEstimator(x^.5, n=nrow(df0_imputed_Teach_group2), alpha=0.05)$CI[1])
# cc1_CI_UB = sapply(cc1, function(x) 
#                .CorrelationCIEstimator(x^.5, n=nrow(df0_imputed_Teach_group2), alpha=0.05)$CI[2])

# Second CCA variate
cc2 = cca_splithalf_teacher$R2_matrix_BinaryOutcomes_Combined$cc2 
# cc2_CI_LB = sapply(cc2, function(x) 
#                .CorrelationCIEstimator(x^.5, n=nrow(df0_imputed_Teach_group2), alpha=0.05)$CI[1])
# cc2_CI_UB = sapply(cc2, function(x) 
#                .CorrelationCIEstimator(x^.5, n=nrow(df0_imputed_Teach_group2), alpha=0.05)$CI[2])

# Third CCA variate
cc3 = cca_splithalf_teacher$R2_matrix_BinaryOutcomes_Combined$cc3
# cc3_CI_LB = sapply(cc3, function(x) 
#                .CorrelationCIEstimator(x^.5, n=nrow(df0_imputed_Teach_group2), alpha=0.05)$CI[1])
# cc3_CI_UB = sapply(cc3, function(x) 
#                .CorrelationCIEstimator(x^.5, n=nrow(df0_imputed_Teach_group2), alpha=0.05)$CI[2])

# Variance Explained by Linear MOdel
LM_VE = cca_splithalf_teacher$R2_matrix_BinaryOutcomes_Combined$LM_R2


Table2 = 
cbind.data.frame(cc1, 
                 cc2, 
                 cc3,
                 LM_VE
                 )

AverageVE = apply(Table2, 2, mean)
Table2 = rbind.data.frame(Table2, AverageVE)
  
Table2 %>% 
          # format(.,nsmall=3, digits=0) %>%
          # mutate_all(.,str_replace_all, pattern = "0\\.", replacement="\\.") %>%
          dplyr::slice(c(match(Outcome_Ordered2, outcomes2),29)) %>% 
          `rownames<-`(c(Outcome_Labels_Ordered2, "Mean")) %>% 
          `colnames<-`(c("cc1","cc2","cc3","LM")) %>%
          knitr::kable(digits=3)



        


rm(cc1,#cc1_CI_LB,cc1_CI_UB,
   cc2,#cc2_CI_LB,cc2_CI_UB,
   cc3,#cc3_CI_LB,cc3_CI_UB,
  LM_VE
  )

```


### Supplementary Alcohol Plots

```{r}

  load(file.path("Data","MCS Data","Processed Data","DataWithExclusionsNoImputations","df0_BothGroups_FINAL.Rdata"))
  
  ##SES and alcohol use - SUPPLEMENTARY MATERIALS
  #Recode variables so that higher alcohol use is greater, and normalise vars
    df0$S1_Parent_AlcoholCurrent_REVERSED = (Convert(df0$S1_Parent_AlcoholCurrent,1:7,7:1))
    df0$S1_Parent_AlcoholPregnant_REVERSED = (Convert(df0$S1_Parent_AlcoholPregnant,1:7,7:1))
    
    df0$S1_Parent_AlcoholCurrent_REVERSED_NORM = (Convert(df0$S1_Parent_AlcoholCurrent,1:7,7:1))
    df0$S1_Parent_AlcoholPregnant_REVERSED_NORM = (Convert(df0$S1_Parent_AlcoholPregnant,1:7,7:1))
  
  # brewer.pal(n = 4, name = "Dark2")
  
  # Parents and children's alcohol consumption (without using normed data)
  # ggplot(data=df0, aes(y=S1_SES_EquivIncome_Norm,x=S1_Parent_AlcoholCurrent_REVERSED)) + geom_hline(yintercept=0, linetype="dashed", col="grey") + geom_smooth(method="lm", se=FALSE, col="grey") + geom_jitter(aes(y=S1_SES_EquivIncome_Norm,x=S1_Parent_AlcoholCurrent_REVERSED-.4),width=.1, height=0, alpha=.2) + 
  #   jtools::theme_apa() + scale_x_continuous(breaks=1:7, labels = c("Never", "<1 Month","1-2 Times a Month","1-2 Times a Week","3-4 Times a Week","5-6 Times a Week", "Every Day")) + 
  #   geom_boxplot(aes(group=S1_Parent_AlcoholCurrent_REVERSED),col="black", fill="#1B9E77", outlier.shape = NA, width = .2, position = position_dodge(width = 0.75), notch = TRUE) + 
  #   coord_flip() + labs(y="Equivilised Income (ADOEDE00) Normalised",x="Alcohol Consumption After Pregnancy (amaldr00)")
  # 
  #   
  # ggplot(data=df0, aes(y=S1_SES_EquivIncome_Norm,x=S1_Parent_AlcoholPregnant_REVERSED)) + geom_hline(yintercept=0, linetype="dashed", col="grey") + geom_smooth(method="lm", se=FALSE, col="grey") + geom_jitter(aes(y=S1_SES_EquivIncome_Norm,x=S1_Parent_AlcoholPregnant_REVERSED-.4),width=.1, height=0, alpha=.2) + 
  #   jtools::theme_apa() + scale_x_continuous(breaks=1:7, labels = c("Never", "<1 Month","1-2 Times a Month","1-2 Times a Week","3-4 Times a Week","5-6 Times a Week", "Every Day")) + 
  #   geom_boxplot(aes(group=S1_Parent_AlcoholPregnant_REVERSED),col="black", fill="#D95F02", outlier.shape = NA, width = .2, position = position_dodge(width = 0.75), notch = TRUE) + 
  #   coord_flip() + labs(y="Equivilised Income (ADOEDE00) Normalised",x="Alcohol Consumption During Pregnancy (amdrof00)") 
  
  # Alcohol Consumption after pregnancy and family income
  p1=
  ggplot(data=df0, aes(y=S1_SES_EquivIncome_Norm,x=S1_Parent_AlcoholCurrent_REVERSED)) + geom_hline(yintercept=0, linetype="dashed", col="grey")  + 
    geom_smooth(aes( y=S1_SES_EquivIncome_Norm,x=S1_Parent_AlcoholCurrent_REVERSED_NORM), method="lm", se=FALSE, col="grey") +
    geom_jitter(aes(y=S1_SES_EquivIncome_Norm,x=S1_Parent_AlcoholCurrent_REVERSED_NORM-.35),width=.095, height=0, alpha=.2) + 
    jtools::theme_apa() + 
    scale_x_continuous(breaks=sort(na.omit(unique(df0$S1_Parent_AlcoholCurrent_REVERSED_NORM))), labels = c("Never", "<1 Month","1-2 Times a Month","1-2 Times a Week","3-4 Times a Week","5-6 Times a Week", "Every Day")) + 
    geom_boxplot(aes(group=S1_Parent_AlcoholCurrent_REVERSED_NORM, y=S1_SES_EquivIncome_Norm,x=S1_Parent_AlcoholCurrent_REVERSED_NORM),col="black", fill="#1B9E77", outlier.shape = NA, width = .18, position = position_dodge(width = 0.75), notch = TRUE) + 
    coord_flip() + labs(y="Equivilised Income (ADOEDE00) Normalised",x="Alcohol Consumption After Pregnancy (amaldr00)") +
    ggtitle("A")
  
  # Alcohol Consumption DURING pregnancy and family income
  p2=
  ggplot(data=df0, aes(y=S1_Parent_AlcoholCurrent_REVERSED_NORM,x=S1_Parent_AlcoholPregnant_REVERSED_NORM)) + geom_hline(yintercept=0, linetype="dashed", col="grey")  + 
    geom_smooth(aes( y=S1_SES_EquivIncome_Norm,x=S1_Parent_AlcoholPregnant_REVERSED_NORM), method="lm", se=FALSE, col="grey") +
    geom_jitter(aes(y=S1_SES_EquivIncome_Norm,x=S1_Parent_AlcoholPregnant_REVERSED_NORM-.35),width=.095, height=0, alpha=.2) + 
    jtools::theme_apa() + 
    scale_x_continuous(breaks=sort(na.omit(unique(df0$S1_Parent_AlcoholPregnant_REVERSED_NORM))), labels = c("Never", "<1 Month","1-2 Times a Month","1-2 Times a Week","3-4 Times a Week","5-6 Times a Week", "Every Day")) + 
    geom_boxplot(aes(group=S1_Parent_AlcoholPregnant_REVERSED_NORM, y=S1_SES_EquivIncome_Norm,x=S1_Parent_AlcoholPregnant_REVERSED_NORM),col="black", fill="#1B9E77", outlier.shape = NA, width = .18, position = position_dodge(width = 0.75), notch = TRUE) + 
    coord_flip() + labs(y="Equivilised Income (ADOEDE00) Normalised",x="Alcohol Consumption During Pregnancy (amdrof00)") +
    ggtitle("B")
  
  #Parent and children's alcohol
  df0$S6_RiskyBehaviours_Alcohol_factor = factor(df0$S6_RiskyBehaviours_Alcohol, levels=c(0,1),labels=c("Drunk Alcohol","Not Drunk Alcohol")) #factorise children's alcohol consumption for simpler plotting
  
  #Tables used to add count information to plots
  Table_1 = table(df0$S6_RiskyBehaviours_Alcohol_factor, df0$S1_Parent_AlcoholCurrent_REVERSED_NORM)
    Table_1 = melt(Table_1)
    Table_1$y = rep(c(.85,.15),7)
  Table_2 = table(df0$S6_RiskyBehaviours_Alcohol_factor, df0$S1_Parent_AlcoholPregnant_REVERSED_NORM)
    Table_2 = melt(Table_2)
    Table_2$y = rep(c(.85,.15),7)
    
  #Parent alcohol consumption after pregnancy and CHILDREN"S consumption
  p3=
  ggplot(data=df0[!is.na(df0$S6_RiskyBehaviours_Alcohol),], aes(x=(S1_Parent_AlcoholCurrent_REVERSED_NORM), fill=S6_RiskyBehaviours_Alcohol_factor)) + 
    geom_bar(position="fill",stat="count", width=.4) + 
    scale_x_continuous(breaks=sort(na.omit(unique(df0$S1_Parent_AlcoholCurrent_REVERSED_NORM))), labels = c("Never", "<1 Month","1-2 Times a Month","1-2 Times a Week","3-4 Times a Week","5-6 Times a Week", "Every Day")) +
    jtools::theme_apa() + theme(axis.text.x = element_text(angle = 90)) +
    labs(x="Alcohol Consumption After Pregnancy (amaldr00)", y = "Children's Alcohol Consumption (Pink = Never)") + 
    geom_text(data=Table_1,aes(y=y,x=Var2,fill=NULL,label=value), angle=90) + theme(legend.position = "none") + 
    scale_fill_manual(values = c("#1B9E77", "#E7298A"))+
    scale_y_continuous(breaks=seq(0,1,by=.25), labels=c("0%","25%","50%","75%","100%")) +
    ggtitle("C")
    
  #Parent alcohol consumption during pregnancy and CHILDREN"S consumption
  p4=
  ggplot(data=df0[!is.na(df0$S6_RiskyBehaviours_Alcohol),], aes(x=(S1_Parent_AlcoholPregnant_REVERSED_NORM), fill=S6_RiskyBehaviours_Alcohol_factor)) + 
    geom_bar(position="fill",stat="count", width=.4) + 
    scale_x_continuous(breaks=sort(na.omit(unique(df0$S1_Parent_AlcoholPregnant_REVERSED_NORM))), labels = c("Never", "<1 Month","1-2 Times a Month","1-2 Times a Week","3-4 Times a Week","5-6 Times a Week", "Every Day")) +
    jtools::theme_apa() + theme(axis.text.x = element_text(angle = 90)) +
    labs(x="Alcohol Consumption During Pregnancy (amdrof00)", y = "Children's Alcohol Consumption (Pink = Never)")+
    geom_text(data=Table_2,aes(y=y,x=Var2,fill=NULL,label=value), angle=90) + theme(legend.position = "none") +
    scale_fill_manual(values = c("#1B9E77", "#E7298A"))+
    scale_y_continuous(breaks=seq(0,1,by=.25), labels=c("0%","25%","50%","75%","100%")) +
    ggtitle("D")
  
  
  # Combine plots

  p1 + p2 + p3 + p4
  
  ggsave(file="Plots/Alcohol_SupplementaryFigure.png", device="png", width = 15, height = 10)
  pdf(file="Plots/Alcohol_SupplementaryFigure.pdf", width=15, height=10)
  p1 + p3 + p2 + p4
  dev.off()
    

```