---
title: "CCA Analyses - Main Script"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---

## Session Info 

I ran the code in a docker container, for better repoducibility :) 

Code to docker image:

> docker pull bignardig/rocker3.6.2:yb64s

> docker run -d -p 8787:8787 -e PASSWORD=YOURPASSWORDHERE -v "/mnt/c/users/.../Paper 2 - Cumulative Risk/Analysis:/home/rstudio/" bignardig/rocker3.6.2:yb64s

Note that the above code works when running ubuntu on windows using WSL2. The /mnt/ part in the path specifies the windows file system. 

I also did the following (in WSL2 ubuntu):

> docker exec -it CONTAINERID bash

Then i run the following:

> ulimit -s unlimited

Most of my CCA analysis code has been moved to its own (in development) R package on github (ccatools), linked below. The code will pull a specific version of that package, so it will be completely reproducible in the future! 

Note that if your running the code from a fresh rocker container, you need to do the following:

> sudo apt-get update  
> sudo apt-get install libxml2
> sudo apt-get install zlib1g-dev
> sudo apt-get install libgsl-dev
> sudo apt-get install xclip 

The last one is for clipr:: to work!

```{r setup, include = FALSE}

packages <- c("knitr","patchwork", "tidyverse", "devtools","patchwork","wesanderson")
install.packages(setdiff(packages, rownames(installed.packages())))  


rm(list=ls(all.names = TRUE))
knitr::opts_chunk$set(cache = TRUE) 
set.seed(10000)
```

```{r}
sessionInfo()
```


## Load Data, Functions and Libraries Required 

```{r, warning=FALSE, results=FALSE, message=FALSE}
source("Script P2S0 - Load Analysis Environment.R")

# Load my own R (work in progress) R package for CCA analyses

if (!("ccatools" %in% installed.packages())) {
  devtools::install_github("giac01/ccatools@bd358f15fdec486a8cb06480fb0bf5dd66ada757") #The @ specifies a specific commit (version) of the package on github
}


# library(usethis)
# library(testthat)
library(ccatools)
library(tidyverse)
library(patchwork)



REPEATS_BOOT = 10000
REPEATS_BOOT
```

## Number of participants

```{r}

DataSets = list(df0_imputed_group1,
                df0_imputed_group2,
                df0_imputed_BothGroups,
                df0_imputed_Teach_group1,
                df0_imputed_Teach_group2,
                df0_imputed_Teach_BothGroups)

sapply(DataSets,nrow) %>%
  `names<-`(c("Training", "Testing", "Combined",
              "Training Teach", "Testing Teach", "Combined Teach"))


```

## Variable Labels 

```{r}
cbind(all_var_labels2, all_var2) %>% kable()

```

## Analysis 0  - Hierarchial cluster analysis of variables

To  aid visualisation, we cluster the predictor and outcome variables into 4 (5 groups including teacher metrics)

```{r, echo=TRUE,results='hide',fig.keep='all'}
distances = stats::dist(t(df0_imputed_BothGroups[,outcomes]), method="manhattan")
  hclust_results = stats::hclust(distances)
  Outcome_Order = hclust_results$order
  Outcome_Ordered = outcomes[Outcome_Order]
  Outcome_Labels_Ordered = outcomes_labels[Outcome_Order]
  plot(hclust_results, hang=-1, main = "Hierarchial Clustering of Outcome Variables")
  Outcome_Cluster = stats::cutree(hclust_results, 4)
# sort(Outcome_Cluster)
  Outcome_Cluster_Labels = Convert(Outcome_Cluster,1:4,c("Behavioural Problems","Mental Health", "Drug-Use", "Cognition"))

# For ease of presentation, teacher's responses are not clustered in the usual way, but just tagged on to the above. 
  Outcome_Cluster2 = c(rep(0,6),Outcome_Cluster)
  Outcome_Ordered2 = c(outcomes2[1:6],Outcome_Ordered)
  Outcome_Labels_Ordered2 = c(outcomes_labels2[1:6],Outcome_Labels_Ordered)
  names(Outcome_Cluster2)[1:6] = outcomes2[1:6]
  Outcome_Cluster_Labels2 = Convert(Outcome_Cluster2,0:4,c("Teacher Ratings","Behavioural Problems","Mental Health", "Drug-Use", "Cognition"))

# not used in results  - but out of curiorsity looked at clustering all outcomes with teacher-reports
# 
#       hclust_results = hclust(dist(t(df0_imputed_Teach[,outcomes2]), method="manhattan"))
#       plot(hclust_results, hang=-1)

#Cluster Predictors
distances = dist(t(df0_imputed_group1[,envvar]), method="manhattan")
hclust_results = hclust(distances)
envvar_Order = hclust_results$order
envvar_Ordered = envvar[envvar_Order]
envvar_Labels_Ordered = envvar_labels[envvar_Order]
# plot(hclust_results, hang=-1)


```

## Analysis 1

### Quick Check - does my cca function  give identical results to stats::cancor ? (the answer is yes)

#### R output 

cancor_Xweights & cancor_Yweights are the normalised (in the linear algebra sense) raw coefficients for a cca model in df0_imputed_group1 ! 

```{r}
cca_cancor = stats::cancor(x=scale(df0_imputed_group1[,envvar]), y=scale(df0_imputed_group1[,outcomes]))


  cancor_Xweights = apply(cca_cancor$xcoef,2, function(x) x/sqrt(sum(x^2)))
  cancor_Yweights = apply(cca_cancor$ycoef,2, function(x) x/sqrt(sum(x^2)))

cca_cancor$cor[1:10]
cancor_Xweights[1:5,1:5]

```

#### ccatools::.cca output 

Result is the same apart from sign difference in loadings, which is why some negative canonical correlations exist when looking at correlations between variate scores. 

```{r}

cca_group1 = ccatools::.cca(X_FIT  = as.matrix(df0_imputed_group1[envvar]),                                               # Data frame of predictor variables (Environmental Risk Factors) from TRAINING dataset
                            Y_FIT  = as.matrix(df0_imputed_group1[outcomes]))
cca_group1$cc_fit
#gb_test$cc_pred
cca_group1$xcoef[1:5,1:5]

rm(cca_group1)

```

We can flip the sign loadings by rotated the weights to align to the R output: 

```{r}

cca_group1 = ccatools::.cca( 
                     X_FIT  = as.matrix(df0_imputed_group1[envvar]),                                               # Data frame of predictor variables (Environmental Risk Factors) from TRAINING dataset
                     Y_FIT  = as.matrix(df0_imputed_group1[outcomes]),
                     ProcrustX = cancor_Xweights[,1:22],
                     ProcrustY = cancor_Yweights[,1:22],
                     ncomp=22
              )
cca_group1$cc_fit
#gb_test$cc_pred
cca_group1$xcoef[1:5,1:5]


```

### Run split half analyses 

Fit Model in training dataset, and then generate canonical variates for testing dataset, and plot correlations between them. 

Figure:
Below diagonical we have correlations between canonical variates. X1-X10 are latent factors extracted from predictor variables, and Y1-Y10 are latent factors extracted from outcome variables. 

```{r, fig.width=8, fig.height=8}
#gb_CCA is defined in script P2S2! 
NVARIATES = 10 # Number of variates to extract 

cca_splithalf_noprocrustes = ccatools::cca_splithalf(
              X_FIT  = df0_imputed_group1[envvar],                                               # Data frame of predictor variables (Environmental Risk Factors) from TRAINING dataset
              Y_FIT  = df0_imputed_group1[outcomes],                                             # Data frame of Outcome Variables from TRAINING dataset
              X_PRED = df0_imputed_group2[envvar],                                               # Data frame of predictor variables (Environmental Risk Factors) from TEST dataset
              Y_PRED = df0_imputed_group2[outcomes],                                             # Data frame of Outcome variables from TEST dataset
              ncomp = NVARIATES)                                                                 # Number of canonical variates to extract  

ccatools::plotcor(cca_splithalf_noprocrustes$model_results$variates, abs_colour = FALSE, reportCI = FALSE, includeN = FALSE) 

```

Because it gets confusing to interpret negative correlations (as most raw variables have been coded so that higher == better), we can flip the extracted CCA loadings to ensure that canonical correlations will be positive. 

An easy way to do this given how the function is coded is to make sure the extracted loadings match the stats::cancor output which automatically corrects for this... 

```{r, fig.width=6, fig.height=6}
NVARIATES = 22 
NVARIATES_Plot = 8
cca_splithalf_procrustes = 
              ccatools::cca_splithalf(
              X_FIT  =      df0_imputed_group1[envvar],                                               # Data frame of predictor variables (Environmental Risk Factors) from TRAINING dataset
              Y_FIT  =      df0_imputed_group1[outcomes],                                             # Data frame of Outcome Variables from TRAINING dataset
              X_PRED =      df0_imputed_group2[envvar],                                               # Data frame of predictor variables (Environmental Risk Factors) from TEST dataset
              Y_PRED =      df0_imputed_group2[outcomes],                                             # Data frame of Outcome variables from TEST dataset
              ProcrustX =   cancor_Xweights[,1:NVARIATES],                                                      # Target matrices used to rotate loadings using procrustes function. 
              ProcrustY =   cancor_Yweights[,1:NVARIATES],
              ncomp  =      NVARIATES)                                                                # Number of canonical variates to extract 

Variates_Plot = cca_splithalf_procrustes$model_results$variates
  colnames(Variates_Plot) = c(paste0("ERF ",1:NVARIATES), paste0("Outcome ",1:NVARIATES))

# Correlation Plot of first 8 variates


Variates_Correlation_Test = 
  Variates_Plot %>% 
    dplyr::select(dplyr::matches("[ ][1-8]{1}$")) %>%
  ccatools::plotcor(., abs_colour = FALSE, reportCI = FALSE, includeN = FALSE) 


Variates_Correlation_Test

save(cca_splithalf_procrustes, file=file.path("Output R Data", "cca_splithalf.Rdata"))
ggsave(file.path("Plots","Variates_Correlation_Test.pdf"), plot=Variates_Correlation_Test, device="pdf", width=6, height=6)
```


### Plot Variate Scores

```{r}
# 
# Variates_Plot$id = 1:nrow(Variates_Plot)
# Variates_Plot_long = tidyr::pivot_longer(Variates_Plot, id)
library(patchwork)

Plot1=
Variates_Plot %>%
apply(.,2,scale) %>%
as.data.frame() %>%
ggplot(., aes(x=`ERF 1`, y=`Outcome 1`)) + 
  geom_point(alpha=.4, shape=16) + 
  jtools::theme_apa() + coord_fixed() + theme(aspect.ratio=1) + 
  labs(x="1st CCA Risk Component",
       y="1st CCA Outcome Component") 

Plot2=
Variates_Plot %>%
apply(.,2,scale) %>%
as.data.frame() %>%
ggplot(., aes(x=`ERF 2`, y=`Outcome 2`)) + 
  geom_point(alpha=.4, shape=16) + 
  jtools::theme_apa() + coord_fixed() + theme(aspect.ratio=1) + 
  labs(x="2nd CCA Risk Component",
       y="2nd CCA Outcome Component") 

Plot3=
Variates_Plot %>%
apply(.,2,scale) %>%
as.data.frame() %>%
ggplot(., aes(x=`ERF 3`, y=`Outcome 3`)) + 
  geom_point(alpha=.4, shape=16) + 
  jtools::theme_apa() + coord_fixed() + theme(aspect.ratio=1) + 
  labs(x="3rd CCA Risk Component",
       y="3rd CCA Outcome Component") 

plot_combined = Plot1 + Plot2 + Plot3 

ggsave(file.path("Plots","CanonicalCorrelations.png"), plot=plot_combined, device="png", width=12, height=7, dpi=600)

ggsave(file.path("Plots","CanonicalCorrelations1.png"), plot=Plot1, device="png", width=4.3, height=4.3, dpi=600)
ggsave(file.path("Plots","CanonicalCorrelations2.png"), plot=Plot2, device="png", width=4.3, height=4.3, dpi=600)
ggsave(file.path("Plots","CanonicalCorrelations3.png"), plot=Plot3, device="png", width=4.3, height=4.3, dpi=600)


```


### Latent Variable (Variate) score correlations within the training sample

I've plotted this here as it nicely illustrates how CCA works! 

```{r, fig.width=6, fig.height=6}
NVARIATES = 8

Variates_Plot = cca_group1$variates[,c(paste0("X",1:NVARIATES),paste0("Y",1:NVARIATES))]
  colnames(Variates_Plot) = c(paste0("ERF ",1:NVARIATES), paste0("Outcome ",1:NVARIATES))

Variates_Correlation_Train =

PlotCorrelationMatrix(Variates_Plot, includeN = FALSE, zerotext = "0", aligntext = FALSE) + ggplot2::theme(legend.position = "#DAECED") + 
        ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1, vjust=1)) + ggplot2::scale_fill_gradient2(low = "#0072B2", 
        mid = "white", high = "#D55E00", midpoint = 0, na.value = "#F5F5F5", guide = "colourbar", aesthetics = "fill") 

Variates_Correlation_Train

ggsave(file.path("Plots","Variates_Correlation_Train.pdf"), plot=Variates_Correlation_Train, device="pdf", width=6, height=6)


```

### Correlation Matrix of all raw data

```{r, fig.width=10, fig.height=10}
plot_data = cbind.data.frame(
                df0_imputed_BothGroups[envvar[envvar_Order]],
                rep(NA, nrow(df0_imputed_BothGroups)),
                df0_imputed_BothGroups[outcomes[Outcome_Order]])
colnames(plot_data) = c(envvar_labels[envvar_Order]," ",outcomes_labels[Outcome_Order])
gp = ccatools::plotcor(plot_data, abs_colour = FALSE, reportCI = FALSE, includeN = FALSE, textadjust = 1.3) + theme(axis.text.x = element_text(angle = 90,hjust=1, vjust=.5))
gp

#Export File 
ggsave(file.path("Plots","SupplementaryFigure1.pdf"), plot=gp, device="pdf", width=10, height=10)
ggsave(file.path("Plots","SupplementaryFigure1.png"), plot=gp, device="png", width=10, height=10, dpi=600)

rm(gp,plot_data)

plot_data = cbind.data.frame(
                df0_imputed_Teach_BothGroups[envvar[envvar_Order]],
                rep(NA, nrow(df0_imputed_Teach_BothGroups)),
                df0_imputed_Teach_BothGroups[Outcome_Ordered2])
colnames(plot_data) = c(envvar_labels[envvar_Order],
                        " ",
                        outcomes_labels2[match(Outcome_Ordered2,outcomes2)])
gp = ccatools::plotcor(plot_data, abs_colour = FALSE, reportCI = FALSE, includeN = FALSE, textadjust = 1.3) + theme(axis.text.x = element_text(angle = 90,hjust=1, vjust=.5))
gp


 
 
#Export File 
ggsave(file.path("Plots","SupplementaryFigure2.pdf"), plot=gp, device="pdf", width=10, height=10)
ggsave(file.path("Plots","SupplementaryFigure2.png"), plot=gp, device="png", width=10, height=10, dpi=600)

rm(gp, plot_data)
```

### Correlation matrix with no numbers

```{r, fig.width=5, fig.height=5}
plot_data = cbind.data.frame(
                df0_imputed_BothGroups[envvar[envvar_Order]],
                rep(NA, nrow(df0_imputed_BothGroups)),
                df0_imputed_BothGroups[outcomes[Outcome_Order]])

# Function to transform data
sqwoosh = function(x, power = 2){
  is.neg = which(x<0)
  out = `^`(abs(x),power)
  out[is.neg] = out[is.neg]*-1
  return(out)
}

#Function which creates a correlation matrix plot of variables - without any labels 
PlotCorrelationMatrix_Reduced = function(dat, Variables_Labels=NULL, textadjust=2){
      Variables = colnames(dat)
      if(is.null(Variables_Labels)){
        Variables_Labels = colnames(dat)
      }
      
      
      matrix_scores = dat
      Mat_Cor =gsub("^0","",gsub("^ +","",gsub("^-0","-", format(cor(matrix_scores, use="pairwise.complete.obs"), digits=0, nsmall=2)))) #Correlation matrix
      Mat_Cor_fill = apply(cor(matrix_scores, use="pairwise.complete.obs"), 2,function(x) sqwoosh(x,.7)) #Correlation matrix for table fill 
      Mat_Cor_fill[lower.tri(Mat_Cor_fill,diag = TRUE)]=NA
      
      #Matrix on Ns per comparison - lower triag 
      Mat_N = sapply(Variables, function(x) 
        sapply(Variables, function(y)
          nrow(na.omit(data.frame(dat[,unique(c(x,y))])))
        )) 
      
      #Create Dataframe For Ggplot to Read 
      PlotMat = Mat_Cor
      PlotMat[lower.tri(PlotMat, diag=TRUE)]=""
      colnames(PlotMat) = Variables_Labels ;  rownames(PlotMat) = Variables_Labels
      
      PlotMat = data.frame(reshape2::melt(PlotMat), stringsAsFactors = FALSE)
      head(PlotMat)
      
      PlotMat$value = (as.character(PlotMat$value))
      PlotMat$ValueFill = as.numeric(t(c(Mat_Cor_fill)))
      PlotMat$Var2 = factor(PlotMat$Var2, levels=rev(levels(PlotMat$Var2)))
      
      
      
      OutPlot = 
        ggplot(data = PlotMat, aes(x=Var1, y=Var2,fill=ValueFill))+# + geom_point(aes(size=value^2,alpha=value^4))+
        geom_tile() + labs(x=NULL, y=NULL) +
         jtools::theme_apa() +
        #scale_fill_brewer(palette=1,na.value="grey")+
        # scale_fill_continuous(na.value="white",low="#EDCB64", high="#B62A3D")+ 
        scale_fill_gradient2(low =  "#0072B2", 
        mid = "white", high =  "#D55E00", midpoint = 0, na.value = "#F5F5F5",  
        guide = "colourbar", aesthetics = "fill") + 
        theme(legend.position = "#DAECED") + 
        theme(axis.title=element_blank(),
                    axis.text=element_blank(),
                    axis.ticks=element_blank()) + coord_fixed()
      
      OutPlot
      
      return(OutPlot)
    }
    
# Plot Data
PlotCorrelationMatrix_Reduced(plot_data, textadjust = 1.3)


#Export File 
ggsave(file.path("Plots","CorMat_BothGroups_NONUM.pdf"), device="pdf", width=5, height=5)
rm(plot_data)
```

### Canonical Correlation point-estimates, CIs, p-values


```{r}


format(cca_splithalf_procrustes$combined_cc, digits=0, nsmall=5)




```



```{r}

# NVARIATES = 15
# 
# cca_splithalf_CI = 
#               gb_CCA_splithalf(
#               X_FIT  = df0_imputed_group1[envvar],                                               # Data frame of predictor variables (Environmental Risk Factors) from TRAINING dataset
#               Y_FIT  = df0_imputed_group1[outcomes],                                             # Data frame of Outcome Variables from TRAINING dataset
#               ProcrustX = cancor_Xweights[,1:NVARIATES],                                         # Rotated the weights JUST so that  
#               ProcrustY = cancor_Yweights[,1:NVARIATES],
#               X_PRED = df0_imputed_group2[envvar],                                               # Data frame of predictor variables (Environmental Risk Factors) from TEST dataset
#               Y_PRED = df0_imputed_group2[outcomes],
#               ncomp=NVARIATES)
# 
# 
# # Internal check for giacomo - check that rotating the results JUST impacts the sign of the canonical correlations & CI
# cca_splithalf_CI_old = 
#               gb_CCA_splithalf(
#               X_FIT  = df0_imputed_group1[envvar],                                               # Data frame of predictor variables (Environmental Risk Factors) from TRAINING dataset
#               Y_FIT  = df0_imputed_group1[outcomes],                                             # Data frame of Outcome Variables from TRAINING dataset
#               ProcrustX = NULL,                                        # Target matrices used to rotate loadings using procrustes function. 
#               ProcrustY = NULL,
#               X_PRED = df0_imputed_group2[envvar],                                               # Data frame of predictor variables (Environmental Risk Factors) from TEST dataset
#               Y_PRED = df0_imputed_group2[outcomes],
#               ncomp=NVARIATES)
# 



# save(cca_splithalf_CI, file=file.path("Output R Data", "cca_splithalf_CI.Rdata"))
# round(cca_splithalf_CI$combined_cc*100)/100

```



## Analysis 2 - CCA loadings and bootstrap estimates of consistency

### Run Model 

```{r, results=FALSE}
set.seed(10)
timeA = base::Sys.time()

NVARIATES = 4
cca_boot = ccatools::coef_boot(
              X_FIT  = df0_imputed_group1[envvar],                                               # Data frame of predictor variables (Environmental Risk Factors) from TRAINING dataset
              Y_FIT  = df0_imputed_group1[outcomes],                                             # Data frame of Outcome Variables from TRAINING dataset
              ProcrustX = cancor_Xweights[,1:NVARIATES],                                        # Target matrices used to rotate loadings using procrustes function. 
              ProcrustY = cancor_Yweights[,1:NVARIATES],
              ncomp  = NVARIATES,                                                                        # Number of variates (latent factors) to extract from X and Y matrices 
              Nboot  =  REPEATS_BOOT                                                         # Number of bootstrap resamples to take (REPEATS_BOOT is defined at the top of the script)
              )  

save(cca_boot, file=file.path("Output R Data", "cca_boot.Rdata"))

timeB = base::Sys.time()

timeB-timeA

```

### print CCA weights 


#### CCA confidence intervals

```{r}

cca_boot$ycoef_Quantiles

xcoef_Quantiles = cca_boot$xcoef_Quantiles

# Shortening row names for easier printing! 
for (i in 1:length(xcoef_Quantiles)){
  rownames(xcoef_Quantiles[[i]]) = substr(rownames(xcoef_Quantiles[[i]]),1,26)
}
xcoef_Quantiles


```


#### CCA Weights (training dataset) 

```{r}
XWeights = cca_group1$xcoef
rownames(XWeights) = substr(envvar_labels,1,26)
colnames(XWeights) = paste0("LV ",1:ncol(XWeights))

XWeights[,1:4]
```

#### CCA Weights (testing dataset) 

```{r}
YWeights = cca_group1$ycoef
rownames(YWeights) = outcomes_labels
colnames(YWeights) = paste0("LV ",1:ncol(YWeights))
YWeights[,1:4]

```


## Run same analyses on teacher dataset

```{r}

NVARIATES = 22 


cca_cancor_teach = stats::cancor(x=scale(df0_imputed_Teach_group1[,envvar]),
                                 y=scale(df0_imputed_Teach_group1[,outcomes2])
                                 )

  cancor_Xweights_teach = apply(cca_cancor_teach$xcoef,2, function(x) x/sqrt(sum(x^2)))
  cancor_Yweights_teach = apply(cca_cancor_teach$ycoef,2, function(x) x/sqrt(sum(x^2)))

# Run Split Half 
cca_splithalf_teacher = ccatools::cca_splithalf(
              X_FIT  =      df0_imputed_Teach_group1[,envvar],                                               # Data frame of predictor variables (Environmental Risk Factors) from TRAINING dataset
              Y_FIT  =      df0_imputed_Teach_group1[,outcomes2],                                             # Data frame of Outcome Variables from TRAINING dataset
              X_PRED =      df0_imputed_Teach_group2[,envvar],                                               # Data frame of predictor variables (Environmental Risk Factors) from TEST dataset
              Y_PRED =      df0_imputed_Teach_group2[,outcomes2],                                             # Data frame of Outcome variables from TEST dataset
              ProcrustX = cancor_Xweights_teach[,1:NVARIATES],                                        # Target matrices used to rotate loadings using procrustes function. 
              ProcrustY = cancor_Yweights_teach[,1:NVARIATES],
              ncomp  =      NVARIATES)                                                                # Number of canonical variates to extract


Variates_Plot = 
cca_splithalf_teacher$model_results$variates %>% 
    dplyr::select(dplyr::matches("[X|Y][1-8]{1}$")) %>%
    `colnames<-` (c(paste0("ERF ",1:8), paste0("Outcome ",1:8))) %>% 
  ccatools::plotcor(., abs_colour = FALSE, reportCI = FALSE, includeN = FALSE) 

  
  
Variates_Plot

save(cca_splithalf_teacher, file=file.path("Output R Data", "cca_splithalf_teacher.Rdata"))

```

#### CCA Weights (teacher dataset) 

```{r}

XWeights = cca_splithalf_teacher$model_results$xcoef
rownames(XWeights) = substr(envvar_labels,1,26)
colnames(XWeights) = paste0("LV ",1:ncol(XWeights))
XWeights[,1:4]


YWeights = cca_splithalf_teacher$model_results$ycoef
rownames(YWeights) = substr(outcomes_labels2,1,26)
colnames(YWeights) = paste0("LV ",1:ncol(YWeights))
YWeights[,1:4]


```


#### Split half cca results (teacher dataset)

```{r}

format(cca_splithalf_teacher$combined_cc, digits=0, nsmall=5)

```



### Bootstrap resampling on teaching data 


```{r, results=FALSE}
set.seed(101)
timeA = base::Sys.time()

NVARIATES = 4                                                                                 #This is lower to reduce risk of bias! 
cca_boot_teach = ccatools::coef_boot(
              X_FIT  = df0_imputed_Teach_BothGroups[envvar],                                               # Data frame of predictor variables (Environmental Risk Factors) from TRAINING dataset
              Y_FIT  = df0_imputed_Teach_BothGroups[outcomes2],                                             # Data frame of Outcome Variables from TRAINING dataset
              ProcrustX = cancor_Xweights_teach[,1:NVARIATES],                                        # Target matrices used to rotate loadings using procrustes function. 
              ProcrustY = cancor_Yweights_teach[,1:NVARIATES],
              ncomp  = NVARIATES,                                                                        # Number of variates (latent factors) to extract from X and Y matrices 
              Nboot  =  REPEATS_BOOT                                                         # Number of bootstrap resamples to take (REPEATS_BOOT is defined at the top of the script)
              )  

save(cca_boot_teach, file=file.path("Output R Data", "cca_boot_teach.Rdata"))


timeB = base::Sys.time()

timeB-timeA

```